title: "Graphics with ggplot2"
author: "Julie"
date: "19-06-19"
output: html_document
---

# Learning ggplot2

load tidyverse
```{r load_package}
library(tidyverse)
```


We're learning ggplot2 It's going to be amazing. 

we extract the link from GitHub "data-science-training/data/OHI_global_data.csv", and then you go to see the "raw data" and paste the link into our read.csv function
```{r data}

ohi_data <-  read.csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/OHI_global_data.csv")

```

we start
```{r start_ggplot}

#ggplot only work with data frame
ggplot(data=ohi_data, aes(x=georegion_one, y=OHI_score))+
  geom_point()

ggplot(data=ohi_data, aes(x=georegion_one, y=OHI_score))+
  geom_jitter(width=0.2)


```

Boxplot
```{r boxplot}

ggplot(data=ohi_data, aes(x=georegion_one))+
  geom_bar()

```

histogram
```{r histogram}
ggplot(data=ohi_data, aes(x=OHI_score))+
  geom_histogram()

```

Multiple geom exploration
```{r multiple geoms}

ohi_summary <- read.csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/OHI_scores_georegion_summary.csv")

ggplot(data=ohi_summary, aes(x=georegions, y= OHI_score_average))+
  geom_bar(stat = 'identity', width=0.5)+
  geom_jitter(data=ohi_data, aes(x=georegion_one, y=OHI_score))


```

Adding a third variable with aes
```{r}

ggplot(data=ohi_data, aes(x=OHI_score, y= HDI, color=coastal_pop))+
  geom_point()
```

Adding a third discrete variable
```{r}
ggplot(data=ohi_data, aes(x=OHI_score, y= HDI, color=georegion_one))+
  geom_point()

```

Themes
```{r}
ggplot(data=ohi_data, aes(x=OHI_score, y= HDI))+
  geom_point()+
  theme_bw()

```

change theme to theme dowload from GitHub
```{r}
source('https://raw.githubusercontent.com/OHI-Science/ohiprep/master/src/R/scatterTheme.txt')       

ggplot(data = ohi_data, aes(x = OHI_score, y = HDI)) + 
  geom_point() + 
  scatterTheme
```

Change labels
```{r}
       
ggplot(data = ohi_data, aes(x = OHI_score, y = HDI, color-georegion_one)) + 
  geom_point() +
  theme(y="OHI core, 2017",
        x="human development Index",
        title="Human development is good",
        color="Georegions")
```

Instale package
```{r}
install.packages("RcolorBrewer")
library(RColorBrewer)
display.brewer.all()

my_palette <- brewer.pal(n=9, "Set3")

```

